The Analogue Method for Precipitation Forecasting: Finding Better Analogue Situations at a Sub-Daily Time Step

### 2016-05-18 Moving temporal window - HESS/template.tex
Corrections from Michel.

\introduction  %% \introduction[modified heading if necessary]

@@

The first method is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}. Searching analogue situations for a target day starts by a preselection step of the potential candidate for analogy. Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects. Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window and at certain hours:

@@

The second reference method adds a subsequent level of analogy on moisture variables (method 2Z-2MI, Table \ref{table:method_2Z-2MI}). This second predictor is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}. When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations. When a second level of analogy is added, a higher number of $N_{1}$ analogues is kept on the first level.

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.3cm]{figures/illustration_moving_window.pdf}
	\end{center}
	\caption{Illustration of the principle of a sliding time window. The bars illustrate the 24~h precipitation totals.}
	\label{fig:principle}
\end{figure}

@@

Figure \ref{fig:changes_S1_analogues} presents the changes in the distributions of the S1 criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogues for the Ulrichen station on the whole calibration period, due to introduction of the STW. The precipitation target remains at before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day). The shapes of the distributions of the conventional approach and the STW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better. An increase in the difference between a fixed window and a sliding window is identifiable, which means that the last analogues are further improved. The latter effect is due to the accumulation of improvements brought by the new analogue situations in the selection.

@@

@@

On the contrary, the summer months have a preference for the initial temporal window (Z500 24h \& Z1000 12h), due to more pronounced diurnal effects which reduces the potential for improvement of the criteria. Other seasons are between these two extremes, which is consistent with their respective improvements. This seasonal effect was observed for each station in a very similar way, and generally even with a larger amplitude than for Ulrichen.

@@

When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogues, but their dates may have changed. In contrast to earlier, both a reduction or an increase of the RMSE analogy criterion values are possible. Indeed, Figure \ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values. Unlike for the first level of analogy, the relative improvement of the RMSE values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude. Once again, the results for the other stations are similar.

@@

The CRPS score can be decomposed into two components, namely sharpness and accuracy. The impact of the STW has been analyzed on these components and the results can be found in Table \ref{table:CRPSS_decomposition_no_recalibration} for the original parameters and in Table \ref{table:CRPSS_decomposition_recalibration} for the re-calibrated methods. The changes are expressed relative to the total CRPS. Both components do not have the same value ranges: accuracy is in our case almost twice the sharpness values. Since the CRPS is considered here and not the CRPSS, improved prediction capacity results in a lower score. A decrease of the score is thus desirable.

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8cm]{figures/illustration_disaggregation.pdf}
	\end{center}
	\caption{Illustration of the generation of 24~h-totals moving averages by means of a proportional distribution.}
	\label{fig:illustration_disaggregation}
\end{figure}

\begin{table}[htb]
	\caption{Values of the CRPSS (\%) skill score for the original and the recalibrated parameters using the STW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& original & recalib. & original & recalib. \\
			\hline
			Ulrichen & 29.13 & 29.61 & 33.15 & 33.45 \\
			Zermatt & 22.17 & 22.80 & 26.72 & 27.43 \\
			Visp & 22.32 & 22.89 & 27.01 & 28.04 \\
			Montana & 29.41 & 30.24 & 33.83 & 34.55 \\
			Sion & 22.98 & 23.41 & 28.57 & 29.15 \\
			Aigle & 29.07 & 29.46 & 34.66 & 35.09 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:disaggregation_proportional}
\end{table}

@@

\begin{table}[htb]
	\caption{Values of the CRPSS (\%) skill score for Zermatt, for the original and the recalibrated parameters using the STW approach on the disaggregated precipitation time series (short and long periods) by means of variables from the reanalysis.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Period} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& original & recalib. & original & recalib. \\
			\hline
			1982-2007 & 22.57 & 23.14 & 27.11 & 27.71 \\
			1961-2008 & 23.81 & 24.38 & 28.42 & 28.86 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:proxy_CRPSS}
\end{table}

>>>>

\introduction  %% \introduction[modified heading if necessary]
\label{sec:introduction}

@@

The first method is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}. Searching analogue situations for a target day starts by a preselection step of the potential candidate for analogy. Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects. Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954}, which is a comparison of gradients, over a certain spatial window and at certain hours:

@@

The second reference method adds a subsequent level of analogy on moisture variables, compared by means of the root-mean-square error (RMSE) (method 2Z-2MI, Table \ref{table:method_2Z-2MI}). This second predictor is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}. When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations. When a second level of analogy is added, a higher number of $N_{1}$ analogues is kept on the first level.

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.3cm]{figures/illustration_moving_window.pdf}
	\end{center}
	\caption{Illustration of the principle of a sliding time window. The larger horizontal bars represent the 24~h precipitation totals.}
	\label{fig:principle}
\end{figure}

@@

Figure \ref{fig:changes_S1_analogues} presents the changes in the distributions of the S1 criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogues for the Ulrichen station on the whole calibration period, due to introduction of the STW. The precipitation target remains as before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day). The shapes of the distributions of the conventional approach and the STW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better. An increase in the difference between a fixed window and a sliding window is identifiable, which means that the last analogues are further improved. The latter effect is due to the accumulation of improvements brought by the new analogue situations in the selection.

@@

\begin{figure}[htb]
	\includegraphics[width=8.3cm]{figures/hours_selection_per_season_Visp.pdf}
	\caption{Distribution of the predictors hours in the selected analogue dates depending on the season, for the Visp station.}
	\label{fig:hours_selection_per_season_Visp}
\end{figure}

@@

On the contrary, the summer months have a preference for the initial temporal window (Z500 24h \& Z1000 12h), due to more pronounced diurnal effects which reduces the potential for improvement of the criteria. Other seasons are between these two extremes, which is consistent with their respective improvements. This seasonal effect was observed for each station in a very similar way, and generally even with a slightly larger amplitude than for Ulrichen (see example of the Visp station in Figure \ref{fig:hours_selection_per_season_Visp}).

@@

When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogues, but their dates have changed. In contrast to earlier, both a reduction or an increase of the RMSE analogy criterion values are possible. Indeed, Figure \ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values. Unlike for the first level of analogy, the relative improvement of the RMSE values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude. Once again, the results for the other stations are similar.

@@

The CRPS score can be decomposed into two components, namely sharpness and accuracy \citep[see][]{Bontron2004}. The impact of the STW has been analyzed on these components and the results can be found in Table \ref{table:CRPSS_decomposition_no_recalibration} for the original parameters and in Table \ref{table:CRPSS_decomposition_recalibration} for the re-calibrated methods. The changes are expressed relative to the total CRPS. Both components do not have the same value ranges: accuracy is in our case almost twice the sharpness values. Since the CRPS is considered here and not the CRPSS, improved prediction capacity results in a lower score. A decrease of the score is thus desirable.

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8cm]{figures/illustration_disaggregation.pdf}
	\end{center}
	\caption{Illustration of the generation of 24~h-totals moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
	\label{fig:illustration_disaggregation}
\end{figure}

\begin{table}[htb]
	\caption{Values of the CRPSS (\%) skill score for the original and the recalibrated parameters (with the sequential method, as described in Section \ref{sec:introduction}) using the STW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& original & recalib. & original & recalib. \\
			\hline
			Ulrichen & 29.13 & 29.61 & 33.15 & 33.45 \\
			Zermatt & 22.17 & 22.80 & 26.72 & 27.43 \\
			Visp & 22.32 & 22.89 & 27.01 & 28.04 \\
			Montana & 29.41 & 30.24 & 33.83 & 34.55 \\
			Sion & 22.98 & 23.41 & 28.57 & 29.15 \\
			Aigle & 29.07 & 29.46 & 34.66 & 35.09 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:disaggregation_proportional}
\end{table}

@@

\begin{table}[htb]
	\caption{Values of the CRPSS (\%) skill score for Zermatt, for the original and the recalibrated parameters (with the sequential method, as described in Section \ref{sec:introduction}) using the STW approach on the disaggregated precipitation time series (short and long periods) by means of variables from the reanalysis.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Period} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& original & recalib. & original & recalib. \\
			\hline
			1982-2007 & 22.57 & 23.14 & 27.11 & 27.71 \\
			1961-2008 & 23.81 & 24.38 & 28.42 & 28.86 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:proxy_CRPSS}
\end{table}
